---
title: Validation of Noncompartmental Analysis Performed by NonCompart R package 
author: Kyun-Seop Bae
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2: default
  pdf_document: default
  html_document: default
---


------

# Introduction

`NonCompart` package can conduct a noncompartmental analysis as closely as possible to the most widely used commercial software for pharmacokinetic analysis, i.e. [Phoenix(R) WinNon-lin(R)](https://www.certara.com/software/pkpd-modeling-and-simulation/phoenix-winnonlin/).
This document provides validation of noncompartmental analysis performed by noncompart r package as compared to the results from the commercial software.

# Results

This script will be stopped if there is any difference between results from NonCompart and WinNonLin printing `Test Failed!`.
Eight comparison tests were performed using `Theoph` and `Indometh` default datasets.


```{r}
library(NonCompart)
RptCfg = read.csv("RptCfg.csv", as.is=TRUE)

Equal = function(Wres, Rres, Tol=0.001)
{
  Wres[,"ID"] = as.character(Wres[,"Subject"])
  ColName0 = colnames(Rres)
  rownames(RptCfg) = RptCfg[,"PPTESTCD"]
  colnames(Rres) = c(ColName0[1], RptCfg[ColName0[-1],"WNL"])
  Inter = intersect(colnames(Wres), colnames(Rres))

  IsSame = TRUE
  for (i in 1:nrow(Wres)) {
    for (j in Inter) {
      R = as.numeric(Rres[i,j])
      W = as.numeric(Wres[i,j])
      if (W != 0) {
        if(abs((R - W)/W) > Tol) {
          print(Wres[i,j])
          print(Rres[i,j])
          IsSame = FALSE
        }
      }
    }
  }
  return(IsSame)
}

Theoph[,"Subject"] = as.numeric(as.character(Theoph[,"Subject"]))
Indometh[,"Subject"] = as.numeric(as.character(Indometh[,"Subject"]))

Wres = read.csv("Final_Parameters_Pivoted_Theoph_Linear.csv")
Rres = tblNCA(Theoph, "Subject", "Time", "conc", dose=320, concUnit="mg/L")
if (!Equal(Wres, Rres)) stop("Test Failed!")

Wres = read.csv("Final_Parameters_Pivoted_Theoph_Log.csv")
Rres = tblNCA(Theoph, "Subject", "Time", "conc", dose=320, down="Log", concUnit="mg/L")
if (!Equal(Wres, Rres)) stop("Test Failed!")

Wres = read.csv("Final_Parameters_Pivoted_Indometh_Linear.csv")
Rres = tblNCA(Indometh, "Subject", "time", "conc", dose=25, adm="Bolus", concUnit="mg/L", R2ADJ=0.8)
if (!Equal(Wres, Rres)) stop("Test Failed!")

Wres = read.csv("Final_Parameters_Pivoted_Indometh_Log.csv")
Rres = tblNCA(Indometh, "Subject", "time", "conc", dose=25, adm="Bolus", down="Log", concUnit="mg/L", R2ADJ=0.8)
if (!Equal(Wres, Rres)) stop("Test Failed!")

Wres = read.csv("Final_Parameters_Pivoted_Indometh_Linear_Infusion.csv")
Rres = tblNCA(Indometh, "Subject", "time", "conc", dose=25, adm="Infusion", dur=0.25, concUnit="mg/L", R2ADJ=0.8)
if (!Equal(Wres, Rres)) stop("Test Failed!")

Wres = read.csv("Final_Parameters_Pivoted_Indometh_Log_Infusion.csv")
Rres = tblNCA(Indometh, "Subject", "time", "conc", dose=25, adm="Infusion", dur=0.25, down="Log", concUnit="mg/L", R2ADJ=0.8)
if (!Equal(Wres, Rres)) stop("Test Failed!")

Wres = read.csv("Final_Parameters_Pivoted_Indometh_Linear_Wrong_Extravascular.csv")
Rres = tblNCA(Indometh, "Subject", "time", "conc", dose=25, concUnit="mg/L", R2ADJ=0.8)
if (!Equal(Wres, Rres)) stop("Test Failed!")

Wres = read.csv("Final_Parameters_Pivoted_Indometh_Log_Wrong_Extravascular.csv")
Rres = tblNCA(Indometh, "Subject", "time", "conc", dose=25, down="Log", concUnit="mg/L", R2ADJ=0.8)
if (!Equal(Wres, Rres)) stop("Test Failed!")
```

# Conclusion 

Nothing happeded and it indicates that **there is no discrepancy** between results from NonCompart and WinNonLin 

\pagebreak

# (APPENDIX) Appendix {-}

# Side by side value comparison

```{r}
Wres = read.csv("Final_Parameters_Pivoted_Theoph_Log.csv")
Rres = tblNCA(Theoph, "Subject", "Time", "conc", dose=320, down="Log", concUnit="mg/L")

library(dplyr)
library(tidyr)

Wres %>% 
  gather(WNL, WinNonLin, -Subject) %>% 
  right_join(RptCfg %>% select(PPTESTCD, WNL)) %>% 
  left_join(Rres %>% as.data.frame() %>% gather(PPTESTCD, NonCompart, -Subject)) %>% 
  select(Subject, PPTESTCD, WNL, WinNonLin, NonCompart) %>% 
  knitr::kable(longtable = TRUE, booktabs = TRUE)
```

# Session Information

```{r}
devtools::session_info()
```


